Analysis PPM-S

### 2020-05-09 production/prod_analysis-cfa.rmd
Plotlikert
El grafico se genera en analisis, es enviado a output/images y llamado desde paper. subo ademas el .css que comente.

>>>>

```{r}
library(ggplot2)
library(reshape2)
library(sjPlot)

dat_merit <- dat04 %>% select("Effort"=perc_effort,"Talent"=perc_talent, "Rich Parents"=perc_wpart, "Contacts"=perc_netw, "Effort"=pref_effort,"Talent"=pref_talent,"Rich Parents"=pref_wpart, "Contacts"=pref_netw)

plotlikert<-plot_likert(dat_merit, c(1,1,1,1,2,2,2,2),
            groups.titles = c("Perceptions","Preferences"),
            geom.colors ="PuBu", 
            axis.labels=c("Effort","Talent","Rich Parents","Contacts"),
            catcount = 4,
            cat.neutral = 3, 
            grid.range  =  c ( 1.2 , 1.4 ),
            values  =  "sum.outside",
            reverse.scale=TRUE)

ggsave(plotlikert,filename = "output/images/plotlikert.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")

```
